%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
%a4paper, % Uncomment for A4 paper size (default is US letter)
11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

% Use the EB Garamond font
% \usepackage{ebgaramond}
\usepackage{textcomp}

%------------------------------------------------

\name{Allen Gueco} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{allen.gueco1@gmail.com | Philadelphia, PA} % A secondary address (optional)

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{Villanova University} \hfill May 2020 \\
B.S.\ in Computer Science \hfill \textit{Villanova, PA} \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{BNY Mellon \textbar{} Pershing}{Jun 2020 - Jan 2024}{Senior Associate, Full Stack Engineer}{Pennington, NJ}
		\item Developed an internal load testing tool to monitor and benchmark existing critical microservices.
		\item Assisted in rewriting critical Angular and Spring Boot components for an internal configuration management tool.
		\item Created and maintaining REST-ful internal APIs and microservices using Spring Boot and its related technologies.
		\item Helped create an internal tool which collect runtime information of Java projects using Agents.
		\item Remediated cyber vulnerabilities and static code scan findings.
		\item Enhanced a Spring Boot microservice that integrates vendor product for providing geolocation info to login services.
		\item Ensured adequate code coverage using Unit and Integration Testing for Java (Mockito, and JUnit) and Angular (Jasmine, Karma, and Cypress) projects.
		\item Worked on Agile-based development teams with members located across US and India.
		\item Containerized frontend and backend applications using Docker and deploying on-prem.
		\item Designed responsive and mobile-friendly login screens for company products.
		\item Maintained and implemented CI/CD pipelines to greatly improve developer workflow.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{AmerisourceBergen Corporation}{Jun 2019 - Aug 2019}{EDI Intern}{Chesterbrook, PA}
		\item Developed an internal tool for the Electronic Data Interchange (EDI) team to ensure data integrity for b2b transactions.
		\item Designed APIs through MuleSoft to provide a REST-ful service for the tool.
		\item Created an Oracle PL/SQL procedure that emails a report based on an ad-hoc query.
	\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Programming Languages & Java, Rust, Kotlin, TypeScript, JavaScript, Python, C\# \\
		Frameworks & Spring, Angular 2+, Angular Material, Reactive Programming \\
		OS & Windows, Linux (Ubuntu), MacOS \\
		Tools \& Technologies & Git, Jira, Confluence, Gradle, Docker, Splunk, BrowserStack, \\
		\phantom & SonarQube, Veracode, IntelliJ, VSCode, Postman, Insomnia, \\
		\phantom & Agile, CI/CD, DevOps \\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

	\textbf{Apolaki}, \textsl{Rust}\\
		A ray tracer library implemented from scratch using Test-Driven Development (TDD) principles.\\
		https://github.com/allengueco/apolaki-rs\\\\
	\textbf{Betaguess}, \textsl{Angular, TailwindCSS}\\
		A Word-of-the-day guessing game.\\
		https://github.com/allengueco/betaguess\\\\ 
\end{rSection}
%----------------------------------------------------------------------------------------

\end{document}
