%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font

%------------------------------------------------

\name{Allen Gueco} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{allen.gueco1@gmail.com | Philadelphia, PA} % A secondary address (optional)

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{Villanova University} \hfill May 2020 \\
	B.S. in Computer Science \hfill \textit{Villanova, PA} \\
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{BNY Mellon \textbar{} Pershing}{June 2020 - Present}{Lead Full Stack Developer}{Pennington, NJ}
		\item Developing an internal load testing tool to monitor and benchmark existing critical microservices.
		\item Creating and maintaining REST-ful APIs and microservices using Spring Boot and its related technologies.
		\item Designing and developing responsive and mobile-friendly login screens for company products.
		\item Helping to create an internal tool which collect runtime information of Java-based projects using Java Agents.
		\item Containerizing various types of frontend and backend applications using Docker and deploying on-prem.
		\item Maintained CI/CD pipelines to greatly improve developer workflow.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Villanova University}{Sep 2019 - May 2020}{Web Application Consultant}{Villanova, PA}
		\item Developed additional features of Villanova University\textquotesingle{}s official mobile app by overhauling the UX/UI.
		\item Assisted in creating a Microsoft Power App that unified information across different campus departments.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{AmerisourceBergen Corporation}{June 2019 - Aug 2019}{EDI Intern}{Chesterbrook, PA}
		\item Assisted the development of an automated testing tool for the Eletronic Data Interchange (EDI) team to ensure data integrity from b2b transactions.
		\item Designed APIs through MuleSoft to provide a REST-ful service for the tool.
		\item Created an Oracle PL/SQL procedure that produces and emails a report based on the result of an ad-hoc query.
	\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Programming Languages & Java, Rust, Python, Kotlin, TypeScript, C\# \\
		Frameworks & Spring Boot, Angular 2+, Pandas, Matplotlib \\
		OS & Windows, Linux (Ubuntu) \\
		Tools \& Technologies & Git, Jira, Docker, Agile, CI/CD, DevOps
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

	\textbf{Apolaki}, {\sl Rust}\\ A ray tracer library implemented from scratch using Test-Driven Development (TDD) principles.\\ https://github.com/allengueco/apolaki-rs\\\\
	\textbf{Movie Recommender}, {\sl Rust}\\ A movie recommender system implemented using user-based collaborative filtering, a neighborhood reduction using covering-based rough sets.\\ https://github.com/allengueco/recommender\\\\

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
